---
title: "HW_10"
author: "Jarrod Pelkofer"
date: "March 27, 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW 20.1-1 a, b, c

```{r}
random <- c(.3039, .7914, .8543, .6902, .3004, .0383)

# a)unbiased coin
flips <- character()
for(i in  random){
  if(i < .50){
    flips <- c(flips, "Heads")
  }
  else{
    flips <- c(flips, "Tails")
  }
}

# b) Pitcher 60% strikes, 40% balls
pitches <- character()
for(i in  random){
  if(i < .60){
    pitches <- c(pitches, "Strike")
  }
  else{
    pitches <- c(pitches, "Ball")
  }
}

# c) traffic light Green 40%, Yellow 10%, Red 50%
lights <- character()
for(i in random){
  if(i < .10){
    lights <- c(lights, 'yellow')
  }else if(i >= .10 & i <.50){
    lights <- c(lights, 'green')
  }else {
    lights <- c(lights, 'red')
  }
}

flips
pitches
lights

```

##HW 20.1-2 a, b
```{r}

#a)
rand <- c(.3004,.0383,.3883,.6052,.2231,.4250,.3729,.7983,.2340,.0082)

weather <- character()
yesterday <- 'clear'

for(r in rand){
  if(yesterday == 'clear' & r >= .20){
    weather <- c(weather, 'clear')
    yesterday <- 'clear'
  }else if(yesterday == 'clear' & r < .20){
    weather <- c(weather, 'rainy')
    yesterday <- 'rainy'
  }else if(yesterday == 'rainy' & r >= .40){
    weather <- c(weather, 'rainy')
    yesterday <- 'rainy'
  }else if(yesterday == 'rainy' & r < .40){
    weather <- c(weather, 'clear')
    yesterday <- 'clear'
  }
}

print("weather part a:")
weather

#b)
set.seed(33)
rand_b <- runif(10, 0, 1)

weather_b <- character()
yesterday_b <- 'clear'

for(b in rand_b){
  if(yesterday_b == 'clear' & b > .20){
    weather_b <- c(weather_b, 'clear')
    yesterday_b <- 'clear'
  }else if(yesterday_b == 'clear' & b <= .20){
    weather_b <- c(weather_b, 'rainy')
    yesterday_b <- 'rainy'
  }else if(yesterday_b == 'rainy' & b > .40){
    weather_b <- c(weather_b, 'rainy')
    yesterday_b <- 'rainy'
  }else if(yesterday_b == 'rainy' & b <= .40){
    weather_b <- c(weather_b, 'clear')
    yesterday_b <- 'clear'
  }
}

print("weather part b:")
weather_b
```


##HW 20.1-3 a, b, c, d, e
```{r}

#a)
two_sold = 4/25
three_sold = 7/25
four_sold = 8/25
five_sold = 5/25
six_sold = 1/25
print(paste(two_sold,three_sold, four_sold,five_sold,six_sold))
#b)
sales <- c(rep(2,4), rep(3,7), rep(4,8), rep(5,5), 6)
avg_sales_over_25_days <- mean(sales)
avg_sales_over_25_days
#c) answer below

#d)
uni = c(.4476, .9713, .0629)
three_day = double()

for(s in uni){
  if(s <.16){
    three_day <- c(three_day, 2)
  }else if(s >= .16 & s < .4399){
    three_day <- c(three_day, 3)
  }else if(s >= .44 & s < .7599){
    three_day <- c(three_day, 4)
  }else if(s >= .76 & s < .9599){
    three_day <- c(three_day, 5)
  }else{
    three_day <- c(three_day, 6)
  } 
}

three_day
mean(three_day)
mean(three_day) - avg_sales_over_25_days


#e)
set.seed(44)
sales_sim <- sample(sales, 300, replace = TRUE)
mean_sim <- mean(sales_sim)
mean_sim

```
a) P(Two Stoves) = 4/25, P(Three Stoves) = 7/25, P(Four Stoves) = 8/25, P(Five Stoves) = 5/25, P(Six Stoves) = 1/25
b) Average of 3.68 stoves
c) Similar to 20.1-1 where probability ranges are assigned to the number of stoves being sold. This is illustrated in part d.
d) .4476 would equal 4 stoves, .9713 would equal 6 stoves, .0629 would equal 2 stoves. This averages to 4 stoves per day which exceeds the 25 day mean by 0.32 stoves
e) The 300 day simulation resulted in an average of 3.613 stoves per day, .067 stoves/day less than the 25 day average.

##HW 20.4-3
```{r}

#a)
print("Part a")
set.seed(22)
runif(3, 25, 75)

#b)
print("Part b")
set.seed(22)
obs <- runif(3, -1, 1)
for(x in obs){
  u <- (1/16)*(1 + x)^4
  print(paste("u =", u, " and x =", x))
}

#c)
print("Part c")
set.seed(22)
obs <- runif(3, 40, 60)
for(x in obs){
  u <- (1/400)*(x-40)^2
  print(paste("u =", u, " and x =", x))
}

```


##HW 20.4-11
```{r}
#a) and b)
y <- c(.2655, .3472, .0248, .9205, .6130)

#line between (7,0) and (9,.2): y = .1x -.7

#line between (9,.2) and (11,.8): y = .3x + -2.5

#line between (11,.8) and (13,1): y = .1x -.3

for(r in y){
  if(r < .2){
    time <- (r+.7)/.1
    print(paste('Uniform Random # = ', r, 'Observation = ', time))
  }else if(r >= .2 & r < .8 ){
    time <- (r + 2.5)/.3
    print(paste('Uniform Random # = ', r, 'Observation = ', time))
  }else{
    time <- (r + .3)/.1
    print(paste('Uniform Random # = ', r, 'Observation = ', time))
  }  
}

```